Energy and exergy analysis of a cruise ship

### 2018-06-21 Manuscript/Figures/dataProcessing.tex
Some updates to the tables

\tikzset{
  frame/.style={
    rectangle, 
    text width=8em, text centered, text = white,
    minimum height=4em,drop shadow,fill=colone,
    rounded corners,
  },
  % INPUT BOXES
  frameInput/.style={
  	trapezium,
  	trapezium left angle=60,
  	trapezium right angle=120,
  	drop shadow,
  	text width=8em,
  	text centered,
  	text = white,
  	fill = colone
  },
% Output BOXES
frameOutput/.style={
	rectangle,
	drop shadow,
	text width=10em,
	text centered,
	text = white,
	fill = coltwo
},
  % THESIS SECTIONS
  frameSections/.style={
  rectangle,
  text width = 16em,
  text = black,
  fill = white,
  font = \sffamily\huge
  },
  % PROCESSES 
  frameProcesses/.style={
  rectangle,
  drop shadow,
  text width = 10em,
  text = white,
  fill = colthree,
  text centered
  },
  % VARIABLE BOXES
  frameVar/.style={
  rectangle,
  text = blue!80,
  text width 8em,
  fill = white,
  text centered,
  rounded corners
  },
  % MAIN DATA FLOWS
  lineData/.style={
  draw=colfour,rounded corners=2mm,-latex
  },
  lineInfo/.style={
	draw=colfour,dashed,rounded corners=2mm,-latex
}    
}

@@

% Entries on the left
\node [frameSections] (section1) at (0,3) {Data collection} ;
\node [frameSections] (section2) at (14,2) {Data processing} ;
\node [frameSections] (section3) at (31,2) {Analysis} ;

@@

% Lines for ship 1
\path [lineData] (input_data.east) -- (process_filtering.west) ;
\path [lineInfo] (input_tech.east) -| (process_filtering.south) ;

@@

% LINE INFO
\path [lineInfo] (11,-6) -| (process_AE.south) ;
\path [lineInfo] (11,-2) -| (process_ME.south) ;
\path [lineInfo] (13.5,-10) -| (process_HTHR.south) ;
\path [lineInfo] (19,-9) -| (process_Q.south) ;
\path [lineInfo] (19,-6) -| (process_Paux.south) ;

% VARIABLES
\node [frameVar] (aa1) at (25,-2.5) {$\dot{W}, \dot{Q}$} ;
\node [frameVar] (aa1) at (25,-5.5) {$\dot{B}$} ;
% \node [frameVar] (aa1) at (25,-6.5) {$\dot{m}, T$} ;

>>>>

\tikzset{
  frame/.style={
    rectangle, 
    text width=8em, text centered, text = white,
    minimum height=4em,drop shadow,fill=colone,
    rounded corners,
  },
  % INPUT BOXES
  frameInput/.style={
  	trapezium,
  	trapezium left angle=60,
  	trapezium right angle=120,
  	drop shadow,
  	text width=8em,
  	text centered,
  	text = white,
  	fill = colone
  },
% Output BOXES
frameOutput/.style={
	rectangle,
	drop shadow,
	text width=10em,
	text centered,
	text = white,
	font = \sffamily\Large,
	fill = coltwo
},
  % THESIS SECTIONS
  frameSections/.style={
  rectangle,
  text width = 16em,
  text = black,
  fill = white,
  font = \sffamily\huge
  },
  % PROCESSES 
  frameProcesses/.style={
  rectangle,
  drop shadow,
  text width = 10em,
  text = white,
  fill = colthree,
  font = \sffamily\Large,
  text centered
  },
  % VARIABLE BOXES
  frameVar/.style={
  rectangle,
  text = blue!80,
  text width 8em,
  fill = white,
  text centered,
  rounded corners
  },
  % MAIN DATA FLOWS
  lineData/.style={
  draw=colfour,rounded corners=2mm,-latex
  },
  lineInfo/.style={
	draw=colfour,dashed,rounded corners=2mm,-latex
}    
}

@@

% Entries on the left
\node [frameSections] (section1) at (1,2) {Data collection} ;
\node [frameSections] (section2) at (15,2) {Data processing} ;
\node [frameSections] (section3) at (29.5,2) {Analysis} ;

@@

% Lines for ship 1
\path [lineData] (input_data.east) -- (process_filtering.west) ;

@@

% LINE INFO
%\path [lineInfo] (11,-6) -| (process_AE.south) ;
%\path [lineInfo] (11,-2) -| (process_ME.south) ;
%\path [lineInfo] (13.5,-10) -| (process_HTHR.south) ;
%\path [lineInfo] (19,-9) -| (process_Q.south) ;
%\path [lineInfo] (19,-6) -| (process_Paux.south) ;
%\path [lineInfo] (input_tech.east) -| (process_filtering.south) ;

% VARIABLES
%\node [frameVar] (aa1) at (25,-2.5) {$\dot{W}, \dot{Q}$} ;
%\node [frameVar] (aa1) at (25,-5.5) {$\dot{B}$} ;
% \node [frameVar] (aa1) at (25,-6.5) {$\dot{m}, T$} ;

### 2018-06-21 Manuscript/Manuscript.tex
Some updates to the tables

The main principles applied to the modeling are presented in the following sections and summarized in Figure \ref{fig:method}, while a more thorough description and validation of the different approaches is presented in the Appendix.

\begin{figure}
	\centering
	\includegraphics[width=0.95\linewidth]{Figures/dataProcessing}
	\caption{Overview of the data processing from inputs to outputs}
	\label{fig:dataprocessing}
\end{figure}

@@

\begin{figure}
	\centering
	\includegraphics[width=0.999\linewidth]{Figures/Heating_cooling_systems}
	\caption{General view of the ship heating and cooling systems}
	\label{fig:ship:general}
\end{figure}

@@

\begin{figure}[htbp]
	\centering
	\includegraphics[width=0.9\linewidth]{Figures/Pie_EnergyDemand}
	\caption{Energy demand, aggregated data for one year of operations}
	\label{fig:Pie_EnergyDemand}
\end{figure}

@@

>>>>

The main principles applied to the modeling are presented in the following sections and summarized in Figure \ref{fig:dataprocessing}, while a more thorough description and validation of the different approaches is presented in the Appendix. The data is first processed to the main and auxiliary engines modules to derive the related energy flows. These are then used to calculate the electric power demand, the energy flows in the cooling systems and, consequently, the heat recovered in the HTHR systems. This information combined is used to determine the heating demand. Finally, all flows thus obtained are aggregated to determine energy and exergy flows and related efficiencies.

\begin{figure}
	\centering
	\includegraphics[width=0.99\linewidth]{Figures/dataProcessing}
	\caption{Overview of the data processing from inputs to outputs}
	\label{fig:dataprocessing}
\end{figure}

@@

\begin{figure}
	\centering
	\includegraphics[width=0.999\linewidth]{Figures/Heating_cooling_systems}
	\caption{General view of the ship heating and cooling systems. The full list of heat exchangers in the heat exchanger network is provided in the Appendix in Table \ref{tab:appendix:HEN}}
	\label{fig:ship:general}
\end{figure}

@@

\begin{figure}[htbp]
	\centering
	\includegraphics[width=0.99\linewidth]{Figures/Pie_EnergyDemand}
	\caption{Energy demand, aggregated data for one year of operations}
	\label{fig:Pie_EnergyDemand}
\end{figure}

@@

\subsubsection{Full list of exchangers in the ship's heat exchanger network}

\begin{table}[hbp!]
\centering
\resizebox{\textwidth}{!}{%
\begin{tabular}{cll}
\toprule
& Identifier & Full name \\
\midrule
\multirow{ 14}{*}{\rotatebox[origin=c]{90}{Low temperature cooling}} & $HEX_{LT1.1}$ & Charge air cooler, LT stage (ME1)  \\
& $HEX_{LT1.2}$ & Lubricating oil cooler (ME1) \\
& $HEX_{LT2.1}$ & Charge air cooler, LT stage (ME3) \\
& $HEX_{LT2.2}$ & Lubricating oil cooler (ME3) \\
& $HEX_{LT3.1}$ & Charge air cooler, LT stage (AE1) \\
& $HEX_{LT3.2}$ & Lubricating oil cooler (AE1) \\
& $HEX_{LT4.1}$ & Charge air cooler, LT stage (AE3) \\
& $HEX_{LT4.2}$ & Lubricating oil cooler (AE3) \\
& $HEX_{LT5}$ & Generator cooler (AE) \\
& $HEX_{LT6}$ & Propeller oil cooler \\
& $HEX_{LT7}$ & Shaft bearing cooler (ME) \\
& $HEX_{LT8}$ & Steam condenser \\
& $HEX_{LT9}$ & Fin stabiliser cooler \\
& $HEX_{LT10}$ & Gearbox cooler \\
\midrule
\multirow{ 9}{*}{\rotatebox[origin=c]{90}{\parbox[c]{3.5cm}{\centering High temperature cooling}}} & $HEX_{HT1.1}$ & Jacket water cooler (ME1) \\
& $HEX_{HT1.2}$ & Charge air cooler, HT stage (ME1) \\
& $HEX_{HT2.1}$ & Jacket water cooler (ME3) \\
& $HEX_{HT2.2}$ & Charge air cooler, HT stage (ME3) \\
& $HEX_{HT3.1}$ & Jacket water cooler  (AE1) \\
& $HEX_{HT3.2}$ & Charge air cooler, HT stage  (AE1) \\
& $HEX_{HT4.1}$ & Jacket water cooler  (AE3) \\
& $HEX_{HT4.2}$ & Charge air cooler, HT stage  (AE3) \\
& $HEX_{HT-HR1}$ & Heat recovery from HT cooling (eng.room1/3) \\
\midrule
\multirow{ 7}{*}{\rotatebox[origin=c]{90}{\parbox[c]{3cm}{\centering Hot water heat recovery system}}} & $HEX_{HT-HR1}$ & Heat recovery from HT cooling (eng.room1/3) \\
& $HEX_{HT-HR2}$ & Heat recovery from HT cooling (eng.room 2/4) \\
& $HEX_{St-HR}$ & Steam heater \\
& $HEX_{HR1}$ & AC-Reating \\
& $HEX_{HR2}$ & AC-Preheating \\
& $HEX_{HR3}$ & Hot water heater \\
& $HEX_{HR4}$ & Technical water generator \\
\midrule 
\multirow{ 8}{*}{\rotatebox[origin=c]{90}{Steam systems}} & $HEX_{HRSG1}$ & Heat recovery steam generator (AE1) \\
& $HEX_{HRSG2}$ & Heat recovery steam generator (AE3) \\
& $HEX_{HRSG3}$ & Heat recovery steam generator (ME3) \\
& $HEX_{HRSG4}$ & Heat recovery steam generator (AE2) \\
& $HEX_{HRSG5}$ & Heat recovery steam generator (AE4) \\
& $HEX_{HRSG6}$ & Heat recovery steam generator (ME2) \\
& $HEX_{AB1}$ & Auxiliary boiler 1 \\
& $HEX_{AB2}$ & Auxiliary boiler 2 \\
\bottomrule
\end{tabular}}
\caption{Full list of exchangers in the ship's heat exchanger networks}
\label{tab:appendix:HEN}
\end{table}
